Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-09 manuscript.tex
Move final figure
Update manuscript to satisfy JGCD

Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
References~\citenum{elmasri2005} and~\citenum{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
Furthermore, the spacecraft model is assumed to remain in a planar orbit.
As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
Reference~\citenum{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
However, the analysis only considered a second order spherical harmonic gravitational potential model. 
Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.

@@

With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
Based on the shape estimate we seek to determine the best location to land. 
In reality, any landing site selection would be based on a wide variety of factors and constraints. 
However we highlight a few which can be determined autonomously and from the shape estimate.
The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_slope.pdf}}%
    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_slope_masked.pdf}}
    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
\end{figure}

The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
Landing sites which are closer will be considered preferentially over those at a larger distance.
\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}%
    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
\end{figure}
We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
\end{figure}
After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

@@

\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_density.pdf}}%
    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_land_density.pdf}}
    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
\end{figure}

@@

The final phase of the simulation is to utilize the estimated shape model and vertically descend to the desired landing site. 
This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
\end{figure}
A number of videos are available at \url{http://bit.ly/shape_reconstruction} which demonstrate these results.
% \todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}

>>>>

Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
\citeauthor{elmasri2005}~\cite{elmasri2005} and \citeauthor{sanyal2004a}~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
Furthermore, the spacecraft model is assumed to remain in a planar orbit.
As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
\citeauthor{misra2015b}~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
However, the analysis only considered a second order spherical harmonic gravitational potential model. 
Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.

@@

With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
Based on the shape estimate we seek to determine the best location to land. 
In reality, any landing site selection would be based on a wide variety of factors and constraints. 
However we highlight a few which can be determined autonomously and from the shape estimate.
The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_slope.pdf}}\\
    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_slope_masked.pdf}}
    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
\end{figure}

The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
Landing sites which are closer will be considered preferentially over those at a larger distance.
\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}\\
    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
\end{figure}
We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
\end{figure}
After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

@@

\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_density.pdf}}\\
    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_land_density.pdf}}
    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
\end{figure}

@@

The final phase of the simulation is to utilize the estimated shape model and vertically descend to the desired landing site. 
This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{dynamic_exploration_castalia_land_asteroid_trajectory.jpg}
    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
\end{figure}
A number of videos are available at \url{http://bit.ly/shape_reconstruction} which demonstrate these results.
% \todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}
